%!TEX program = xelatex
%!TEX root = ../thesis.tex
\acknowledgments

Firstly, I would like to express my great thanks to my supervisor, Prof. Ming LIU, the Director of Ram-Lab, Robotics Institute in UST, who gave me a chance to join such a great technical and academic platform. He deserves my deepest gratitude for taking me into the group, providing excellent facilities and a wonderful, inspiring atmosphere. I admire his diligence and the pursuit of excellence, which also gave me much encouragement.

Furthermore, I would like to thank all the great people I met in the lab. Thanks to Qing LIANG for guiding my first project. Special thanks to Peng YUN, who spent time helping compose my proposal and gave me lots of suggestions during my thesis development. Thanks to Usman Maqbool Bhutta, Yuxuan LIU, who shared computer programming techniques with me. I owe a lot to you guys. I would also thank many other people in the lab, which I may not be able to show the long list of their names, for the practical and interesting weekly discussions we had during this long time, Jianhao JIAO, Lei TAI, and more. I would also like to honor friends from other schools, Xutan PENG, who suggested a lot during my thesis writing, and Yan MENG, who kept encouraging me.

UST is where creativities, connections, and possibilities happen. Thanks to all the lecturers, including my supervisor Ming LIU, for the great courses I took. These courses strengthened my knowledge and academic background. I want to give my deep appreciation to Prof. Yuan YAO, whose deep learning course leads me into the AI world and gives me much theoretical thinking. Prof. Yuan YAO also generously shared computational resources with me, where many experimental results yielded, including those in this thesis.

Special thanks to my confidant friends Ginny XU, Haoshuo LIU, Yuzhou Hu, Shijia HUANG, Yunxiang YAO, Yuchao HUANG, and Yu HUANG, for the cherishable fun we had together reading books and digesting the news. We also shared knowledge from multidisciplinary fields with each other, which greatly broadened everyone's sights. Thanks to Cong BAI, Zhiyuan QI, Junqiang WU, and many other friends who lived with me during my time at school.

Thanks to my colleagues, especially my mentor in my intern company, for concerning my thesis schedule. Thanks to the administrative and student service in UST.

Finally, I would like to thank my mother and her friends because I always received a positive attitude, and they gave me much encouragement. Thank my father for the financial and spiritual support. I love and appreciate my family.

\endacknowledgments
